---
title: "how to knitr"
author: "me"
output: pdf_document
---
```{r setup, include = FALSE}
# set global chunk options: all images will be 7x5 inches
library(knitr)
opts_chunk$set(fig.width = 7, fig.height = 5)
opts_chunk$set(tidy.opts = list(width = 70,width.cutoff = 70), tidy = TRUE)
options(digits = 4)
# set seed
set.seed(123)
```

<!-- Kommentare sind moeglich mit HTML Kommentaren
<!-- Based on knitr-minimal.Rmd on http://yihui.name/knitr/demo/minimal/ -->

# Abstract

# Introduction

This is a minimal example of using **knitr** to produce a _PDF_ file from _Markdown_. The original version can be found at the knitr [Website](http://yihui.name/knitr/demo/minimal/).

# Related work

# Dataset

# Exploratory analysis



Add libraries
```{r libraries}
# import libraries
library(psych)
library(corrplot)
library(moments)
```
Now we write some code chunks directly in this markdown file.
```{r load}
# Clean console output and environment
rm(list=ls())
cat("\014") 
# Set local path
path_data <- "C:\\ETH\\StatsLab\\data\\"
# Load files
master_data <- readRDS(paste(path_data,"mastertable.rds",sep=""))
log_data <-  readRDS(paste(path_data,"logDataAnonym.rds",sep=""))
course_data <-  readRDS(paste(path_data,"quizList.rds",sep=""))
exam_data <-  readRDS(paste(path_data,"exam.rds",sep=""))
```

```{r exploratory analysis - 1part}
# Formatting data - log data
col_log <- c( "idVollstName", "idBetroffNutzer","Zeit", "Ereigniskontext", "Komponente" ,"Ereignisname", "Beschreibung")
log_data <- log_data[,col_log] 
log_data$Zeit <- as.POSIXct(log_data$Zeit, format = "%d.%m.%Y %H:%M", tz = "")

# Select ids that have grades
id_students <- unique(c(master_data$id))
log_data <- log_data[log_data$idVollstName %in% id_students ,]

# Difference of students interacted with moodle and those who not
NROW(id_students) - NROW(unique(log_data$idVollstName))

# Remove students who did not interact with moodle and went to the exam
id_students_not_participated <- c(setdiff(id_students,log_data$idVollstName))
exam_data <- exam_data[!(exam_data$id %in% id_students_not_participated),]
master_data <- master_data[!(master_data$id %in% id_students_not_participated),]

# Plot data - participation per quiz
table_quiz <- table(master_data$quiz_nr)
plot(table_quiz, ylab ="Frequency", xlab="Quiz", col = "blue", main = "Participation per quiz")

# Plot data - grade distribution
hist(exam_data$Grade, breaks = 10, main = "Distribution of Grades", xlab= "Grades", col = "blue")

# Table summary of grades
grades_dist <- cbind(mean(exam_data$Grade),sd(exam_data$Grade),
                     skewness(exam_data$Grade), kurtosis(exam_data$Grade))
points_dist <- cbind(mean(exam_data$Total),sd(exam_data$Total),
                     skewness(exam_data$Total), kurtosis(exam_data$Total))
distr <- rbind(grades_dist,points_dist)
colnames(distr) <- c("Mean", "Std. deviation", "Skewness", "Kurtosis")
rownames(distr) <- c("Grades","Points")
knitr::kable(distr, align = 'c')
```

```{r exploratory analysis - 2part}
# prepare data and remove ids from students and courses
log_data$Beschreibung <- gsub('[[:digit:]]+|The user with id+|id.*|with.*
                              |[[:punct:]]|^\\s+|\\s+$|\n|\\n', "" 
                              , log_data$Beschreibung)
table_analysis <-  as.data.frame(table(log_data$idVollstName,log_data$Komponente,log_data$Beschreibung))
grades <- as.matrix(exam_data[order(exam_data$id), c("Total")])

# Check length of the matrices
nid <-  NROW(unique(table_analysis$Var1))
ncomp <- NROW(unique(table_analysis$Var2))
nstatus <-  NROW(unique(table_analysis$Var3))

# Determine correlations and format row names
comp_names <- paste0( gsub('OU+|\\s+|\\s+$',"",
                           rep(as.character(
                             unique(table_analysis$Var2)))),
" - ", rep(as.character(unique(table_analysis$Var3)),each = ncomp))
count_test <-  matrix(c(table_analysis$Freq),nrow= nid, ncol= ncomp*nstatus)
colnames(count_test) <- comp_names
count_select <- count_test[, colSums(count_test)> 5]

#Perform t-test for the correlation
NROW(count_select)
NROW(grades)
test_holm <- corr.test(count_select,grades,adjust="holm")

# Draw table with t-tests
corr_log <- as.data.frame(test_holm$r)
corr_test_log  <- as.data.frame(test_holm$p)
order_asc_log <- order(corr_log, decreasing = TRUE)
names_log <- row.names(corr_log)[order_asc_log]
corr_log_matrix <- cor(count_select[,order_asc_log])
corr_test_log <- round(corr_test_log[order_asc_log,],digits = 4)
corr_log <- round(corr_log[order_asc_log,], digits = 4)
colnames(corr_log_matrix) <- seq(NCOL(corr_log_matrix))
summary_corr <- as.data.frame(cbind(names_log,colnames(corr_log_matrix),corr_log,corr_test_log))
colnames(summary_corr) <- c("Description","Index","Coefficient","p-value")
knitr::kable(summary_corr, align = c('l'))

# Plot correlations
colnames(corr_log_matrix) <- seq(NCOL(corr_log_matrix))
rownames(corr_log_matrix) <- seq(NCOL(corr_log_matrix))
corrplot(corr_log_matrix)
```
We can also produce plots. The corresponding outputs are automatically inserted in our output document. We use the built-in dataset `cars`. 

```{r myplot, fig.cap = "\\label{mylabel}Your nice caption here."}
par(mar = c(4, 4, .1, .1))
with(mtcars, {
  plot(mpg ~ hp, pch = 20, cex = 2, col = 'darkgray')
  lines(lowess(hp, mpg))
})
x <- 2
```

In Figure \ref{mylabel} we can observe that ...

### Inline Code

So called **inline R code** is also supported, e.g. the value of `x` is `r x` and today is `r date()`. What about a rounded random number, like `r round(rnorm(1), 2)`? Wait, why doesn't it change?

## Math

LaTeX math can be used as usual: $f(\alpha, \beta) \propto x^{\alpha-1}(1-x)^{\beta-1}$. We can also write $$2^2 + y^2 = 1.$$

## Misc

### Indenting
You can indent code chunks so they can nest within other environments such as lists.

1. the area of a circle with radius x
    ```{r foo}
    2^2 * pi
    ```
2. OK, that is great!

### Tables
We can also produce pretty tables of data frames
```{r table}
knitr::kable(swiss[1:10,], caption = "The first 10 rows of the `swiss` dataset.")
```

Alternatively, we can build a table ourselves manually (here with centered columns).

ETH Zurich   | ETH Lausanne
:----------: | :-----------:
`r rnorm(3)`      | Cell 2
Cell 3       | Cell 4

# Results

# Conclusion

# Recommendations

# Acknowledgments


## Conclusions
Markdown is super easy to write. Go to **knitr** [homepage](http://yihui.name/knitr) for more details.
